SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-11-24 toplas26/examples.tex
checkpoint

We add coercions and typing assertions to the $\ttt{secopen}$ function
to specify properties of secure openings. After noninteractively
summing a wire value $\ttt{x}$ and a random Beaver triple value
$\ttt{x++a}$, the federation can publicly open the value since it is
masked by the random value. This is expressed using the coercion
$\ttt{as RECON(x) +  r[x++a]@3}$. The coercion then allows the
opened value to be declared $\ttt{public}$.

In the \ttt{mult} function, each client $\ttt{i}$ symmetrically
computes:
$$
\ttt{((m[z++"d"] * m[y]) + (-m[z++"e"] * m[z++"a"]) + m[z++"c"])@i}
$$
Since $\ttt{m[z++"d"]@i : public}$ and $\ttt{m[z++"e"]@i : public}$
are both established by $\ttt{secopen}$, and
$\ttt{m[y]@i}$, $\ttt{m[z++"a"]@i}$, and $\ttt{m[z++"c"]@i}$ are
all declared to be shares in preconditions, we have that each
of the shared computations $\ttt{(m[z++"d"] * m[y])@i}$ and $\ttt{(-m[z++"e"] * m[z++"a"])@i}$
are shares, so the gate outputs are shares, and this will
be successfully checked by syntax-directed $\Vdash$ type checking that
results from the declaration $\ttt{[m[z]@i1,m[z]@i2] : shares}$.

@@

In this code we use a convention where shared values $\ttt{x}$ are
represented as a 3-tuple of values, MAC, and keys, where the value and
MAC of client \ttt{1} are $\ttt{m[x++"s"]@1}$ and $\ttt{m[x++"m"]@1}$
respectively, and the corresponding key is $\ttt{m[x++"k"]@2}$ is held
by client \ttt{2}. The correctness condition of this 3-tuple is
$\ttt{MACOK}(x,2,1)$. The same is true symmetrically, so $\ttt{MACed}$
establishes both sides of the correctness condition.  In general,
these are used in gate preconditions to assume that the MAC conditions
hold for input shares, and output shares are $\ttt{MACed}$. The
homomorphic properties that preserve $\ttt{MACed}$ness, especially in
\ttt{mult}, are perhaps even more complex than the algebraic
correctness of gates, so it is very beneficial to verify them
compositional especially for large circuits.

Our code is written so that share MACs are checked for when they are
\ttt{open}ed by both clients, specified by the appropriate
$\ttt{assert}$ included in the protocol. This ensures malicious
security of secure openings and outputs. As is standard in BDOZ/SPDZ,
we assume that input values, MACs, and keys are distributed to clients
by a pre-processing protocol.

>>>>

We add coercions and typing assertions to the $\ttt{secopen}$ function
to specify properties of secure openings. After noninteractively
summing the secret-shared wire value $\ttt{RECON(x)}$ and Beaver triple value
$\ttt{r[x++a]@3}$, the federation can publicly open the result since it is
masked by the random value. This is expressed using the coercion
$\ttt{as RECON(x) +  r[x++a]@3}$. The coercion then allows the
securely opened value to be declared $\ttt{public}$.

In the \ttt{mult} function, each client $\ttt{i}$ symmetrically
computes:
$$
\ttt{((m[z++"d"] * m[y]) + (-m[z++"e"] * m[z++"a"]) + m[z++"c"])@i}
$$
Since $\ttt{m[z++"d"]@i\,:\,public}\ $ and $\ \ttt{m[z++"e"]@i\,:\,public}$
are both established by $\ttt{secopen}$, and
$\ttt{m[y]@i}$, $\ttt{m[z++"a"]@i}$, and $\ttt{m[z++"c"]@i}$ are
all declared to be shares in preconditions, we have that each
of the shared computations $\ttt{(m[z++"d"] * m[y])@i}$ and $\ttt{(-m[z++"e"] * m[z++"a"])@i}$
are shares, so the gate outputs are shares, and this will
be successfully checked by syntax-directed $\Vdash$ type checking that
results from the declaration $\ttt{[m[z]@i1,m[z]@i2]\,:\,shares}$.

@@

In this code we use a convention where shared values $\ttt{x}$ are
represented as a 3-tuple of values, MAC, and keys, where the value and
MAC of client \ttt{1} are $\ttt{m[x++"s"]@1}$ and $\ttt{m[x++"m"]@1}$
respectively, and the corresponding key $\ttt{m[x++"k"]@2}$ is held by
client \ttt{2}. The correctness condition of this 3-tuple is
$\ttt{MACOK}(x,2,1)$. The same is true symmetrically, so the
$\ttt{MACed}$ predicate establishes both sides of the correctness
condition.  In general, this predicate is used in gate preconditions
to assume that the MAC conditions hold for input shares, and in
postconditions to ensure that output shares are $\ttt{MACed}$. The
homomorphic properties that preserve $\ttt{MACed}$ness, especially in
\ttt{mult}, are perhaps even more complex than the algebraic
correctness of gates, so it is beneficial to verify them compositional
especially for large circuits.

Our code is written so that share MACs are checked for when they are
\ttt{open}ed by both clients, specified by the appropriate
$\ttt{assert}$ included in the protocol. This ensures malicious
security of secure openings and outputs. As is standard in BDOZ/SPDZ,
we assume that input values, MACs, and keys are distributed to clients
by a pre-processing protocol with relevant postconditions
declared in the preconditions of $\ttt{main}$ (as in Figure
\ref{fig-beaver} with respect to Beaver triples).
